---
title: "R Notebook"
output: html_notebook
---

This is an example webscrapping in R. Full tutorial here: https://www.business-science.io/code-tools/2019/10/07/rvest-web-scraping.html?utm_source=feedburner&utm_medium=twitter&utm_campaign=Feed%3A+business-science+%28www.business-science.io%29

Here’s the workflow I used to web scrape the Specialized Data and create an application:

Start with URL of Specialized Bicycles

Use rvest and jsonlite to extract product data

Clean up data into “tidy” format using purrr and stringr

Visualize product prices with ggplot2

The website is: 

```{r}
# Load libraries
library(robotstxt) # get and check robots.txt files
library(rvest)     # HTML Hacking & Web Scraping
library(jsonlite)  # JSON manipulation
library(tidyverse) # Data Manipulation
library(xopen)     # Opens URL in Browser
library(knitr)     # Pretty HTML Tables
```

```{r}
get_robotstxt("https://www.specialized.com")
rbt <- robotstxt("https://www.specialized.com")
rbt$bots
rbt$permissions

rbt$crawl_delay

# are we allowed to scrape?
paths_allowed("https://www.specialized.com/us/en/shop/bikes/c/bikes?q=%3Aprice-desc%3Aarchived%3Afalse&show=All")

url <- "https://www.specialized.com/us/en/shop/bikes/c/bikes?q=%3Aprice-desc%3Aarchived%3Afalse&show=All"
#read the page
page <- read_html(url)
```

```{r}
page
```

```{r}
#using Dev tools in chrome find out the main class of json data. you will need to add the "." before the calss name
page %>% 
  rvest::html_nodes(".product-list__item-wrapper")
```

```{r}
#extract the attribute within this node that contains json data
json_data <- page %>% 
  html_nodes(".product-list__item-wrapper")%>%
  html_attr("data-product-ic")

json_data
```

```{r}
#convert json data to tibble
json_data %>% 
  fromJSON() %>%
  as_tibble()
```

this gives parsing error.


```{r}
# Make Function to iterate over everything and analyse errors separatly
from_json_to_tibble <- function(json) {
    json %>%
        fromJSON() %>%
        as_tibble()
}
```

```{r}
json_data[1] %>%
    from_json_to_tibble()
```

```{r}
bike_data_list <- json_data %>%
    map(safely(from_json_to_tibble)) 
```


```{r}
bike_data_list[1]
```

```{r}
#extract errors
bike_data_list %>%
  # Grab just the $error elements
    map(~ pluck(., "error")) %>%
    # Convert from list to tibble
    enframe(name = "row") %>%
    # Return TRUE if element has error
    mutate(is_error = map(value, function(x) !is.null(x))) %>%
    # Unnest nested list
    unnest(is_error) %>%
    # Filter where error == TRUE
    filter(is_error)
```

```{r}
json_data[218] %>%
  str_replace('22.5\\" TT', '22.5 TT') %>%
    from_json_to_tibble()
```

```{r}
json_data[218] %>%
  str_replace('22.5\\" TT', '22.5 TT') %>%
  str_replace('\\"BMX / Dirt Jump\\"','BMX / Dirt Jump')%>%
    from_json_to_tibble()
```

```{r}
json_data[[286]]
```

```{r}
#both same errors so just add str_replace and re-run
bikes_data <- json_data %>%
  str_replace('22.5\\" TT', '22.5 TT') %>%
  str_replace('\\"BMX / Dirt Jump\\"','BMX / Dirt Jump') %>%
  map_dfr(from_json_to_tibble)
```

```{r}
bikes_data
```

```{r}
bikes_data <- janitor::remove_empty(bikes_data)
```



```{r}
bikes_data <- bikes_data %>%
  mutate_all(funs(replace(., .=='', NA)))

bikes_data <- janitor::remove_empty(bikes_data)
bikes_data
```

# rename cols to make them more friendly

```{r}
table(bikes_data$dimension5)
```

```{r}
bikes_data <- bikes_data %>% mutate(dimension6 = fct_recode(dimension6,"S-Works" = "S-Works/S-Works"))
bikes_data <- bikes_data %>% mutate(dimension8 = fct_recode(dimension8,"Men/Women" = "Men/Men/Women"))
bikes_data <- bikes_data %>% mutate(dimension2 = fct_recode(dimension2,"Mountain" = "Mountain/Mountain"))
bikes_data <- bikes_data %>% mutate(dimension3 = fct_recode(dimension3,"Epic EVO" = "Epic EVO/Epic EVO"))
bikes_data <- bikes_data %>% mutate(dimension5 = fct_recode(dimension5,"Cross Country" = "Cross Country/Cross Country"))

bikes_data <- bikes_data %>% rename("gender" = "dimension8",
                      "edition" = "dimension6",
                      "category" = "dimension2",
                      "bike_or_frameset" = "dimension1",
                      "product_family" = "dimension3",
                      "experience" = "dimension5",
                      "price_usd" = "price") %>%
  select(-currencyCode,-brand)
bikes_data
```

# Now bring in other tech specification per bike by opening up their respective web links

```{r}
# base_url <- "https://www.specialized.com/us/en/shop/bikes/c/bikes?q=%3Aprice-desc%3Aarchived%3Afalse&show=All"
# tbl_url <- "https://www.specialized.com/us/en/s-works-stumpjumper-st-27-5/p/157592?color=236250-157592"
# page <- read_html(tbl_url)
# 
# #do it for one:
# # checking if can get col headers
# page %>% html_nodes("table") %>% html_nodes(".product__specs-table-entry")  %>% html_nodes(".product__specs-table-key") %>%  html_text() %>%
#   as.data.frame() %>%
#   rename("spec" = ".")
# 
# # easier way to do it is:
# spec <- page %>% html_nodes(".product__specs-table-key") %>% html_text() %>% str_replace_all(pattern = "\n","")
# value <- page %>% html_nodes(".product__specs-table-value") %>% html_text() %>% str_replace_all(pattern = "\n","")
# 
# data.frame(bike_name = "my_name",spec, value)%>%
#   spread(spec,value) %>%
#   select(sort(names(.)))

# get all tables data in one vector
#page %>% html_nodes("td") %>% html_text() %>% str_replace_all(pattern = "\n","")

specs <- list()
s <- html_session(url)

for (i in bikes_data$name) {
  if(!(i %in% c("Women's Tarmac Disc Expert","Riprock Expert 24","Fatboy 24","Fatboy 20","Riprock Comp 24","Men's Rockhopper Sport"))){
  print(paste("Getting data for:", i))
   product_page <- s %>% follow_link(i) %>% read_html()
   #print(product_page)
   spec <- product_page %>% html_nodes(".product__specs-table-key") %>% html_text() %>% 
                                          str_replace_all(pattern = "\n","") %>%
                                          str_trim() %>%
                                          str_to_upper()
   value <- product_page %>% html_nodes(".product__specs-table-value") %>% html_text() %>% str_replace_all(pattern = "\n","") %>%
                   str_trim()
 
 specs[[i]] <- data.frame(bike_name = i,spec, value)%>%
              spread(spec,value)%>%
              select(sort(names(.)))
  }
}
length(specs)
```

```{r}
bind_rows(specs)
head(specs[[1]]) %>% inner_join(bikes_data,by = c("bike_name"="name"))
specs %>% map(~inner_join(.,bikes_data,by = c("bike_name"="name")))

bike_names <- set_names(bikes_data$name)

bike_names %>% map(~inner_join(bikes_data,specs))
```

```{r}
specs[["S-Works Roubaix - Shimano Dura-Ace Di2"]] %>% names
```


```{r}
specs_data <- data.table::rbindlist(specs, fill = TRUE)
```

```{r}
bikes_data <- bikes_data %>% left_join(specs_data,by = c("name" = "bike_name"))
```

```{r}
bikes_data
```



